### 2019-05-21 2-Chapters/2-Chapter/chapter2.tex
Starting to quote & rewrite the theorems for the lower bounds.

\subsection{Regret lower bounds: do not detail too much, don't explain the tools behind the results}

>>>>

\subsection{Regret lower bounds}

We remind in this section two results about bandit algorithms \emph{cannot} do:
first a worst case result that states that any algorithm can perform as badly as $\Omega(\sqrt(K T))$ on a certain problem instance (a result from \cite{Auer02NonStochastic}),
then a problem-dependent lower-bound that states that any algorithm suffers a regret at least $\Omega(\log T)$ on any problem (from \cite{LaiRobbins85}).
In a certain family of problems, \eg, $K$ Bernoulli distributed arms, the difficulty of a problem is characterized by a measure that depends only on the arms means. This measure of difficulty of a problem is hidden in the $\Omega$ notation of the lower-bound.
For more details, see Chapter~2 in \cite{Slivkins2019}.
In all this section, we restrict to stationary stochastic bandits with $K\geq2$ arms.

\paragraph{Worst-case lower-bound in $\sqrt{T}$}

The following theorem was proven in \cite{Auer02NonStochastic}.

\begin{theorem}\label{thm:2:worstCaseLowerBound}
    For 
\end{theorem}

\paragraph{Problem-dependent lower-bound in $\log T$}

The following two theorems were proven in \cite{LaiRobbins85}.

First, let $\cI$ denote the set of all problem instances, with hypotheses that there are $K \geq 2$ arms whose rewards lie in $[0,1]$.

\begin{theorem}\label{thm:2:firstLogTLowerBound}
    No algorithm $\cA$ can achieve a regret $R^{\cA}(T) = \smallO{c_I \log(T)}$ for all problem instances $I \in \cI$,
    where this notation means that the ``constant'' $c_I$ can depend on the problem instance $I$ (\eg, on the means and on $K$) but not on the time horizon $T$.
\end{theorem}

Then we consider algorithms that uniformly efficient, meaning that we rule out algorithms that can achieve low regret on some problem instance while achieving linear regret on other instances.
In particular, it is necessary to rule out algorithms that always pick the same arms, as on some problem instance such fixed-arm algorithm can achieve zero regret.
For instance, the \UCB{} algorithm is uniformly efficient.

\begin{defn}[Uniformly efficient algorithm]\label{def:2:uniformlyEfficientAlgorithm}
    An algorithm $\cA$ is \emph{uniformly efficient} if it satisfies
    \begin{equation}
        R^{\cA}(T) \leq \bigO{C_{I,\alpha} T^{\alpha}}
    \end{equation}
    for any value $\alpha>0$ and any problem instance $I\in \cI$,
    where this notation means that the ``constant'' $C_{I,\alpha}$ can depend on the problem instance $I$ and on $\alpha$, but not on the time horizon $T$.
\end{defn}

Now we can state the second logarithmic lower-bound, for algorithms in this family:

\begin{theorem}\label{thm:2:secondLogTLowerBound}
    Let $\cA$ denote a uniformly efficient algorithm,
    and $I$ an arbitrary problem instance.
    For this instance,
    there exists a constant $C_I$ depending only on the problem $I$,
    and a time $T_0$ such that
    \begin{equation}
        \forall T \geq T_0,
        \;\;\;
        R^{\cA}(T) \geq C_I \log(T).
    \end{equation}
\end{theorem}

% do not detail too much, don't explain the tools behind the result
